CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-19 paper.Rmd
Updated acknowledgements.
Updated paper.Rmd

| Package | Purpose |
|:--------|:--------|
| [IEATools][link-ieatools]             | Converts [IEA EWEB][link-ieaeweb] data to RUVY matrices in [matsindf][link-matsindf] data frames |
| [MWTools][link-mwtools]               | Converts [ILO][link-ilo] and [FAO][link-fao] data to RUVY matrices of human and animal muscle work in [matsindf][link-matsindf] data frames |
| [Recca][link-recca]                   | Performs `R` energy conversion chain analysis |
| [PFUSetup][link-pfusetup]             | Identifies input and output locations for the [PFUDatabase][link-pfudatabase] and [PFUAggDatabase][link-pfuaggdatabase] pipelines |
| [PFUPipelineTools][link-pfupipelinetools] | Provides basic functionality for all PFU pipelines |
| [PFUDatabase][link-pfudatabase]       | Provides a [targets][link-targets] pipeline to create a data frame of RUVY matrices |
| [PFUAggDatabase][link-pfuaggdatabase] | Provides a [targets][link-targets] pipeline to aggregate RUVY matrices |
| [CLPFUDatabase][link-clpfudatabase]   | A metapackage (like `tidyverse`) to quickly load all packages for the CL-PFU database |

@@

```{r, eval=FALSE}
# (1) Purchase, download, and store IEA EWEB data in the correct location.
#     Sample data for two countries (Ghana and South Africa) 
#     and two years (1971 and 2000) are included (with permission)
#     at the correct location in the repository for this paper.
# (2) Download FAO and ILO data for muscle work calculations
#     via the included script.
#     This download step is needed only once, and
#     downloaded data are stored in the repository 
#     for this paper.
source(file.path("ExampleFolder", "DownloadScripts", "download_mw_data.R"))

@@

M.K.H. acknowledges the support of Calvin University for 
a sabbatical during which he developed the PSUT framework
and course releases during which he wrote many of the `R` packages
described in this paper.
Z.M.'s time was funded by 
the UK Research Council under EPSRC Fellowship award EP/R024254/1.
E.A.'s time was funded by 
the University of Leeds (School of Earth and Environment).
M.K.H., Z.M., and E.A. are grateful for support and encouragement
from Paul E. Brockway (University of Leeds).
It is Paul's EPSRC fellowship that provided the need for the software
described in this paper.

>>>>

| Package | Purpose |
|:--------|:--------|
| [IEATools][link-ieatools]             | Converts [IEA EWEB][link-ieaeweb] data to RUVY matrices in [matsindf][link-matsindf] data frames |
| [MWTools][link-mwtools]               | Converts [ILO][link-ilo] and [FAO][link-fao] data to RUVY matrices of human and animal muscle work in [matsindf][link-matsindf] data frames |
| [Recca][link-recca]                   | Performs `R` energy conversion chain analysis |
| [PFUSetup][link-pfusetup]             | Identifies input and output locations for the [PFUDatabase][link-pfudatabase] and [PFUAggDatabase][link-pfuaggdatabase] pipelines |
| [PFUPipelineTools][link-pfupipelinetools] | Provides basic functionality for all PFU pipelines |
| [PFUDatabase][link-pfudatabase]       | Provides a [targets][link-targets] pipeline to create a data frame of RUVY matrices |
| [PFUAggDatabase][link-pfuaggdatabase] | Provides a [targets][link-targets] pipeline to aggregate RUVY matrices |
| [CLPFUDatabase][link-clpfudatabase]   | A metapackage (like `tidyverse`) to quickly load all package dependencies for the CL-PFU database |

@@

```{r, eval=TRUE}
library(devtools)
# (0) Use the metapackage to install all dependencies.
#     This package installation step is needed only once.
devtools::install_github("EnergyEconomyDecoupling/CLPFUDatabase")

# (1) Purchase, download, and store IEA EWEB data in the correct location.
#     Sample data for two countries (Ghana and South Africa) 
#     and two years (1971 and 2000) are included (with permission)
#     at the correct location in the repository for this paper.
# (2) Download FAO and ILO data for muscle work calculations
#     via the included script.
#     This download step is needed only once, and
#     downloaded data are stored in the repository 
#     for this paper.
source(file.path("ExampleFolder", "DownloadScripts", "download_mw_data.R"))

@@

M.K.H. acknowledges the support of Calvin University for 
a sabbatical during which he developed the PSUT framework
and course releases during which he wrote many of the `R` packages
described in this paper.
Z.M.'s time was funded by 
the UK Research Council under EPSRC Fellowship award EP/R024254/1.
E.A.'s time was funded by 
the University of Leeds (School of Earth and Environment).
M.K.H., Z.M., and E.A. are grateful for support and encouragement
from Dr. Paul E. Brockway (University of Leeds).
It was Dr. Brockway's EPSRC fellowship that provided the need for the software
described in this paper.
